---
title: "hamstrbacon: An Interface Between rbacon and hamstr."
author: Andrew M. Dolman
date: "`r Sys.Date()`"
output:
  github_document:
    html_preview: true
editor_options: 
  chunk_output_type: console
---

-------------------------------


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE, autodep = TRUE,
  fig.width = 9,
  dev = "png",
  dev.args = list(type = "cairo-png"),
  dpi = 300
)
```


## Installation

**hamstrbacon** can be installed directly from Github

```{r, eval=FALSE}
if (!require("remotes")) {
  install.packages("remotes")
}

remotes::install_github("earthsystemdiagnostics/hamstrbacon")
```


## Using **hamstr**

Examples using the example core "MSB2K" from the [rbacon](https://cran.r-project.org/web/packages/rbacon/index.html) package.


```{r setup, message=FALSE}
library(hamstrbacon)

set.seed(20200827)
```




### Fitting age-models with **rbacon** via **hamstrbacon**


```{r}
MSB2K <- hamstr::MSB2K

hambac_1 <- hamstr_bacon(id = "tst", 
                         depth = MSB2K$depth,
                               obs_age = MSB2K$age,
                               obs_err = MSB2K$error,
                               thick = 5, cc = 1,
                         close.connections = FALSE)
```


```{r}
plot(hambac_1)
```

```{r}
summary(hambac_1)
```

```{r}
predict(hambac_1)
```

```{r}
plot(hambac_1, type = "acc")
```

If you want specific depths you can ask for them and the age models will be linearly interpolated

```{r}
spec_depths <- predict(hambac_1, depth = c(10:15))

spec_depths

```

Summary also works after interpolation

```{r}
summary(spec_depths)
```



### References

*  Blaauw, Maarten, and J. Andrés Christen. 2011. Flexible Paleoclimate Age-Depth Models Using an Autoregressive Gamma Process. Bayesian Analysis 6 (3): 457-74. doi:10.1214/ba/1339616472.










