---
title: "Using and comparing hamstr_bacon"
author: "Andrew M. Dolman"
date: "`r Sys.Date()`"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, autodep = TRUE)
```

```{r}
library(hamstr)
```


# Compare hamstr models with Bacon models fit using the hamstr_bacon interface


## Using the example dataset from Bacon


Calibrate the radiocarbon ages for hamstr

```{r, warning=FALSE}
MSB2K_cal <- calibrate_14C_age(MSB2K, age.14C = "age", age.14C.se = "error")
```


First run a hamstr model for comparison.


```{r}
hamstr_10_10 <- hamstr(depth = MSB2K_cal$depth,
                   obs_age = MSB2K_cal$age.14C.cal,
                   obs_err = MSB2K_cal$age.14C.cal.se,
                   K = c(10, 10),
                   cores = 3)
```

```{r}
plot(hamstr_10_10, plot_diagnostics = FALSE)
```


Then run a hamstr_bacon model. Remember to pass the uncalibrated radiocarbon dates to hamstr_bacon as Bacon will do the calibration.

```{r}
hambac_5 <- hamstr_bacon(id = "sdf", 
                         depth = MSB2K_cal$depth,
                               obs_age = MSB2K_cal$age,
                               obs_err = MSB2K_cal$error,
                               thick = 5, cc = 1, 
                         close.connections = FALSE)

plot(hambac_5)

```

The plot method works for hamstr_bacon models too.

```{r, warning=FALSE}
plot(hambac_5,
     # plot the individual iterations rather than a summary, and only plot 30
     summarise = FALSE,
     n.iter = 30)
```


## Getting the age-model realisations and summaries

Summarise the age models at the modelled depths

```{r}
summary(hambac_5)
```


Get all the iterations with predict()

```{r}
predict(hambac_5)
```


If you want specific depths you can ask for them and the age models will be linearly interpolated

```{r}
spec_depths <- predict(hambac_5, depth = c(10:15))

spec_depths

```

Summary also works after interpolation

```{r}
summary(spec_depths)
```


















